---
title: 'Beyond Human Babesiosis: Prevalence and Association of Babesia Coinfection and Mortality in the United States, 2015-2022: a Retrospective Cohort Study'
'
author: "Paddy Ssentongo, MD, PhD"
output:
  html_document:
    pdf_print: paged
  pdf_document: default
---

```{r setup, include=FALSE,warning=FALSE,echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(tinytex.verbose = TRUE)
```


```{r, message=FALSE,echo=FALSE}
library(jtools)
library(tmap)
library(meta)
library(metafor)
library(RISmed)
library(reticulate)
library(dplyr)
library(tibble)
library(stringr)
library(tidytext)
library(ggplot2)
library(tm)
library(RColorBrewer)
library(lme4)
library(survival)
library(sjPlot)
library(sjlabelled)
library(sjmisc)
library(survminer)
library(haven)
library(Cairo)
```


```{r}
rm(list=ls())
dat=read.csv("OFID2024_ssentongo2024.csv", header = T)
dat <- dat[ which(dat$year_diagnosis>'2014'),]
datt <- dat[ which(dat$year_diagnosis<'2023'),]

old=read_sas("remaining_vars_raw01_sentongo2024.sas7bdat")
dat=merge(dat, old, by.x="patient_id", by.y="patient_id", all.x=TRUE)


```

# Temporal distribution of cases: Figure 1
```{r,out.width="100%", out.height="500%", eval=FALSE}

b=datt%>%
  mutate(Month_diagnosis2 = factor(month.abb[Month_diagnosis2], levels = month.abb)) %>%
ggplot(aes(x= Month_diagnosis2,  group=year_diagnosis), color="blue") + 
    geom_bar()+
  #facet_wrap(~ Groups_cat, labeller = new_labels,ncol = 2)+
  facet_wrap(~ year_diagnosis,ncol = 8)+
  
theme(legend.position="top")+
 theme(text = element_text(size = 18))+
   xlab("Month of Infection") + ylab("Number of Babesia infection")
  scale_fill_viridis_d()

b
```


##Table 1------------------------------------------------------------

#Age
```{r}
# Age
summary(dat$age)
sd(dat$age, na.rm = T)

group_by(dat, dat$Coinfection) %>%
  summarise(
    count = n(),
    median = median (age, na.rm = TRUE),
    mean = mean(age, na.rm = TRUE),
    max = max(age, na.rm = TRUE),
    min = min(age, na.rm = TRUE),
    sd = sd(age, na.rm = TRUE),
    IQR = IQR(age, na.rm = TRUE))

res <- t.test(age~dat$Coinfection, data = dat,exact = FALSE)
res
```


#Parasitemia

```{r}
summary(dat$Parasitemia)
sd(dat$Parasitemia, na.rm = T)

group_by(dat, dat$Coinfection) %>%
  summarise(
    count = n(),
    median = median (Parasitemia, na.rm = TRUE),
    mean = mean(Parasitemia, na.rm = TRUE),
    max = max(Parasitemia, na.rm = TRUE),
    min = min(Parasitemia, na.rm = TRUE),
    sd = sd(Parasitemia, na.rm = TRUE),
    IQR = IQR(Parasitemia, na.rm = TRUE))

res <- t.test(Parasitemia~Coinfection, data = dat,exact = FALSE)
res
```



# Co-infection
```{r}
table(dat$Coinfection)
```


#Sex
```{r}
table(dat$sex)
tab <- with(dat, table(Coinfection,sex))
tab
prop.table(tab, margin = 1)*100
chisq.test(tab)
```


# race 
```{r}
table(dat$race)
tab <- with(dat, table(Coinfection,race))
tab
prop.table(tab, margin = 1)*100
chisq.test(tab)
```



# Obesity
```{r}
table(dat$Obesity)
tab <- with(dat, table(Coinfection,Obesity))
tab
prop.table(tab, margin = 1)*100
chisq.test(tab)
```

# Asplenia
```{r}
table(dat$Asplenia)
tab <- with(dat, table(Coinfection,Asplenia))
tab
prop.table(tab, margin = 1)*100
chisq.test(tab)
```


# RA
```{r}
table(dat$RA)
tab <- with(dat, table(Coinfection,Rheumatoid.Arthritis))
tab
prop.table(tab, margin = 1)*100
chisq.test(tab)
```



# All cancer
```{r}
#NHL

dat = dat %>% mutate(across(contains("Any_cancer"), ~replace(., is.na(.), 0)))

table(dat$Any_cancer)
tab <- with(dat, table(Coinfection,Any_cancer))
tab
prop.table(tab, margin = 1)*100
chisq.test(tab)
```




# Solid Malignancy
```{r}
table(dat$Solid_Tumor)
tab <- with(dat, table(Coinfection,Solid_Tumor))
tab
prop.table(tab, margin = 1)*100
chisq.test(tab)
```
# Lymphoma
```{r}
table(dat$Lymphoma)
tab <- with(dat, table(Coinfection,Lymphoma))
tab
prop.table(tab, margin = 1)*100
chisq.test(tab)
```

# Lymphoma: NHL
```{r}
dat = dat %>% mutate(across(contains("Non_Hodgins_lymphoma"), ~replace(., is.na(.), 0)))

table(dat$Non_Hodgins_lymphoma)
tab <- with(dat, table(Coinfection,Non_Hodgins_lymphoma))
tab
prop.table(tab, margin = 1)*100
chisq.test(tab)
```


# Lymphoma: HL
```{r}
dat = dat %>% mutate(across(contains("Hodgins_lymphoma"), ~replace(., is.na(.), 0)))

table(dat$Hodgins_lymphoma)
tab <- with(dat, table(Coinfection,Hodgins_lymphoma))
tab
prop.table(tab, margin = 1)*100
chisq.test(tab)
```




# HIV
```{r}
table(dat$HIV)
tab <- with(dat, table(Coinfection,dat$HIV))
tab
prop.table(tab, margin = 1)*100
chisq.test(tab)
```
# Liver disease
```{r}
table(dat$Liver.disease)
tab <- with(dat, table(Coinfection,Liver.disease))
tab
prop.table(tab, margin = 1)*100
chisq.test(tab)
```

# Kidney disease
```{r}
table(dat$Chronic.Kidney.Disease)
tab <- with(dat, table(Coinfection,Chronic.Kidney.Disease))
tab
prop.table(tab, margin = 1)*100
chisq.test(tab)
```


# Diabetes 
```{r}
table(dat$Diabetes)
tab <- with(dat, table(Coinfection,Diabetes))
tab
prop.table(tab, margin = 1)*100
chisq.test(tab)
```


# COPD
```{r}
table(dat$COPD)
tab <- with(dat, table(Coinfection,COPD))
tab
prop.table(tab, margin = 1)*100
chisq.test(tab)
```

# HTN
```{r}
table(dat$Hypertension)
tab <- with(dat, table(Coinfection,dat$Hypertension))
tab
prop.table(tab, margin = 1)*100
chisq.test(tab)
```


# CHF
```{r}
table(dat$CHF)
tab <- with(dat, table(Coinfection,CHF))
tab
prop.table(tab, margin = 1)*100
chisq.test(tab)
```


# Atovaquone
```{r}
table(dat$Atovaquone)
tab <- with(dat, table(Coinfection,Atovaquone))
tab
prop.table(tab, margin = 1)*100
chisq.test(tab)
```



# Azithromycin
```{r}
table(dat$Azithromycin)
tab <- with(dat, table(Coinfection,Azithromycin))
tab
prop.table(tab, margin = 1)*100
chisq.test(tab)
```


# Clindamycin
```{r}
table(dat$Clindamycin)
tab <- with(dat, table(Coinfection,Clindamycin))
tab
prop.table(tab, margin = 1)*100
chisq.test(tab)
```



# Quinine
```{r}
table(dat$Quinine)
tab <- with(dat, table(Coinfection,Quinine))
tab
prop.table(tab, margin = 1)*100
chisq.test(tab)
```

# Doxy
```{r}
dat = dat %>% mutate(across(contains("doxycycline"), ~replace(., is.na(.), 0)))

table(dat$doxycycline)
tab <- with(dat, table(Coinfection,doxycycline))
tab
prop.table(tab, margin = 1)*100
chisq.test(tab)
```


##Figure 2: Bargraph showing Overall co-infection, Lyme, Eh, Ana-----------------------------------------
# Lyme_disease
```{r}
table(dat$Lyme_disease)


res <- prop.test(x = 1427, n = 3521, p = 0.5, correct = FALSE)
res
# Printing the results
res 
tab <- with(dat, table(Coinfection,Lyme_disease))
tab
prop.table(tab, margin = 1)*100
chisq.test(tab)

```



# Anaplasmosis
```{r}
table(dat$Anaplasmosis)

res <- prop.test(x = 11, n = 3521, p = 0.5, correct = FALSE)
res
tab <- with(dat, table(Coinfection,Anaplasmosis))
tab
prop.table(tab, margin = 1)*100
chisq.test(tab)
```



# Ehrlichia
```{r}
table(dat$Ehlichia)
res <- prop.test(x = 131, n = 3521, p = 0.5, correct = FALSE)
res

tab <- with(dat, table(Coinfection,Ehlichia))
tab
prop.table(tab, margin = 1)*100
chisq.test(tab)
```


#Coinfection
```{r}
table(dat$Coinfection)

res <- prop.test(x = 1472, n = 3521, p = 0.5, correct = FALSE)
res

```

# Deaths
```{r}

table(dat$Death2)

res <- prop.test(x = 48, n = 3521, p = 0.5, correct = FALSE)
res


```



# Region
```{r}
tab <- with(dat, table(Coinfection,patient_regional_location))
tab
prop.table(tab, margin = 1)*100
chisq.test(tab)
```



# ARDS
```{r}
table(dat$ARDS)
tab <- with(dat, table(Coinfection,ARDS))
tab
prop.table(tab, margin = 2)*100
chisq.test(tab)
```

# MOF
```{r}
# Multiorgan failure
table(dat$MOF)
tab <- with(dat, table(Coinfection,MOF))
tab
prop.table(tab, margin = 2)*100
chisq.test(tab)
```


# DIC
```{r}
table(dat$DIC)
tab <- with(dat, table(Coinfection,DIC))
tab
prop.table(tab, margin = 2)*100
chisq.test(tab)
```



# Survival analysis: 90 day mortality with coinfection (either Lyme or/ and Ana/ or/and Ehrl)-------------------------------
```{r}

fit2 <- survfit(Surv(dat$Time, Death90) ~ factor(Coinfection), data = dat)

a=ggsurvplot(fit2,
             pval = T, conf.int = F,
             risk.table = TRUE, # Add risk table
             risk.table.col="strata",
              title="A",
             surv.scale = "percent", 
             tables.theme = theme_cleantable(),
             ylab = "Cumulative Mortality (%) ",
             xlab = "Days since infection",
             ggtheme = theme_bw(), # Change ggplot2 theme
             break.time.by = 5, 
             #palette = "npg", 
             pval.coord = c(0, 0.025),
             legend.title = "Coinfection status",
            # palette = c("blue","maroon"),
             palette = c("red","black"),
             xlim = c(0, 90),
             ylim = c(0, .025),
             curv.size = 5, 
             risk.table.height = 0.25,
             censor=T,
             #fun = "event",
             fun="cumhaz",
             risk.table.y.text.col=F,
             legend.labs = c("Babesiosis only", "Coinfection"))

a


```





# Survival analysis: 30 day mortality with coinfection (either Lyme or/ and Ana/ or/and Ehrl)-------------------------------
```{r}

fit2 <- survfit(Surv(dat$Time, Death30) ~ factor(Coinfection), data = dat)

ab=ggsurvplot(fit2,
             pval = T, conf.int = F,
             risk.table = TRUE, # Add risk table
             risk.table.col="strata",
              title="A",
             surv.scale = "percent", 
             tables.theme = theme_cleantable(),
             ylab = "Cumulative Mortality (%) ",
              xlab = "Days since infection",
             ggtheme = theme_bw(), # Change ggplot2 theme
             break.time.by = 5, 
             #palette = "npg", 
             pval.coord = c(0, 0.025),
             legend.title = "Coinfection status",
            # palette = c("blue","maroon"),
             palette = c("red","black"),
             xlim = c(0, 30),
             ylim = c(0, .025),
             curv.size = 5, 
             risk.table.height = 0.25,
             censor=T,
             #fun = "event",
             fun="cumhaz",
             #surv.median.line = "hv"
             risk.table.y.text.col=F,
             legend.labs = c("Babesiosis only", "Coinfection"))

ab


pdf("figs/SupplFig2.pdf", width = 10)
print(ab, newpage = FALSE)
dev.off()

```



# Survival analysis: 90 day mortality with coinfection with Lyme-------------------------------
```{r}

fit2 <- survfit(Surv(dat$Time, Death90) ~ factor(dat$LYME_IN_12), data = dat)

b=ggsurvplot(fit2,
             pval = T, conf.int = F,
             risk.table = TRUE, # Add risk table
             risk.table.col="strata",
              title="B",
             surv.scale = "percent", 
             tables.theme = theme_cleantable(),
             ylab = "Cumulative Mortality",
             xlab = "Days since infection",
             ggtheme = theme_bw(), # Change ggplot2 theme
             break.time.by = 5, 
             #palette = "npg", 
             pval.coord = c(0, 0.025),
             legend.title = "Coinfection status",
            # palette = c("blue","maroon"),
             palette = c("red","black"),
             xlim = c(0, 90),
             ylim = c(0, .025),
             curv.size = 5, 
             risk.table.height = 0.25,
             censor=T,
             #fun = "event",
             fun="cumhaz",
             risk.table.y.text.col=F,
             legend.labs = c("Babesiosis only", "Coinfection with Lyme disease"))

b




```




# Survival analysis: 90 day mortality with Ehlirchia--------------------------------
```{r}

fit2 <- survfit(Surv(Time, Death90) ~ factor(dat$Ehlichia), data = dat)

c=ggsurvplot(fit2,
             pval = T, conf.int = F,
             risk.table = TRUE, # Add risk table
             risk.table.col="strata",
              title="C",
             surv.scale = "percent", 
             tables.theme = theme_cleantable(),
             ylab = "Cumulative Mortality",
              xlab = "Days since infection",
             ggtheme = theme_bw(), # Change ggplot2 theme
             break.time.by = 5, 
             #palette = "npg", 
             pval.coord = c(0, 0.025),
             legend.title = "Coinfection status",
            # palette = c("blue","maroon"),
             palette = c("red","black"),
             xlim = c(0, 90),
             ylim = c(0, .03),
             curv.size = 5, 
             risk.table.height = 0.25,
             censor=T,
             #fun = "event",
             fun="cumhaz",
             risk.table.y.text.col=F,
             legend.labs = c("Babesiosis only", "Coinfection with ehrlichiosis"))
c

```


# Survival analysis: 90 day mortality with coinfection with Anaplasmosis----------------------------
```{r}

fit2 <- survfit(Surv(dat$Time, Death90) ~ factor(Anaplasmosis), data = dat)

d=ggsurvplot(fit2,
             pval = T, conf.int = F,
             risk.table = TRUE, # Add risk table
             risk.table.col="strata",
              title="D",
             surv.scale = "percent", 
             tables.theme = theme_cleantable(),
             ylab = "Cumulative Mortality",
             xlab = "Days since infection",
             ggtheme = theme_bw(), # Change ggplot2 theme
             break.time.by = 5, 
             #palette = "npg", 
             pval.coord = c(0, 0.025),
             legend.title = "Coinfection status",
            # palette = c("blue","maroon"),
             palette = c("red","black"),
             xlim = c(0, 90),
             ylim = c(0, .025),
             curv.size = 5, 
             risk.table.height = 0.25,
             censor=T,
             #fun = "event",
             fun="cumhaz",
             risk.table.y.text.col=F,
             legend.labs = c("Babesiosis only", "Coinfection with anaplasmosis"))

d


```


```{r}
splots <- list(a,b,c,d)

# Arrange multiple ggsurvplots and print the output
LL=arrange_ggsurvplots(splots, print = TRUE, labels = c("A","B", "C","D"),
 nrow = 2,  ncol = 2, risk.table.height = 0.4)

tiff("figs/Fig4.TIF", width=14000, height=8000, res=600, compression = "lzw")
#pdf("figs/Fig4.pdf", width = 24,height = 15)
print(LL)
dev.off()

```






# unadjustedOR for 90- mortality
```{r}
m1 <- glm(Death90 ~ factor(Coinfection), data =  dat,family=binomial(link = logit))

summary(m1)

aa=exp(cbind(OR = coef(m1), confint(m1)))

f=plot_model(m1, show.values = TRUE, value.offset = .3)
summ(m1,exp = TRUE, digit=4)
```




#aOR for 90- mortality
```{r}
m1 <- glm(Death90 ~ factor(Coinfection)+age+sex+Asplenia+CHF+COPD+Diabetes+Hypertension+Chronic.Kidney.Disease+Lymphoma+Rheumatoid.Arthritis+Obesity+Depression+Blood_Loss_Anemia+Simple_Blood_Transfusion,  data =  dat,family=binomial(link = logit))

summary(m1)


aa=exp(cbind(OR = coef(m1), confint(m1)))



f=plot_model(m1, show.values = TRUE, value.offset = .3)
summ(m1,exp = TRUE, digit=4)
```




# Unadjusted OR for 30- mortality
```{r}
m1 <- glm(Death30 ~ factor(Coinfection), data =  dat,family=binomial(link = logit))

summary(m1)


aa=exp(cbind(OR = coef(m1), confint(m1)))



f=plot_model(m1, show.values = TRUE, value.offset = .3)
summ(m1,exp = TRUE, digit=4)
```




# aOR for 30- mortality
```{r}
m1 <- glm(Death30 ~ factor(Coinfection)+age+sex+Asplenia+CHF+COPD+Diabetes+Hypertension+Chronic.Kidney.Disease+Lymphoma+Rheumatoid.Arthritis+Obesity+Depression+Blood_Loss_Anemia+Simple_Blood_Transfusion,  data =  dat,family=binomial(link = logit))

summary(m1)


aa=exp(cbind(OR = coef(m1), confint(m1)))



f=plot_model(m1, show.values = TRUE, value.offset = .3)
summ(m1,exp = TRUE, digit=4)
```




# HR for 90- d mortality
```{r}
m1 <- coxph(Surv(Time, Death90) ~ factor(Coinfection)+age+sex+Asplenia+CHF+COPD+Diabetes+Hypertension+Chronic.Kidney.Disease+Lymphoma+Rheumatoid.Arthritis+Obesity+Depression+Blood_Loss_Anemia+Simple_Blood_Transfusion,  data =  dat)

summary(m1)

aa=exp(cbind(OR = coef(m1), confint(m1)))
aa

plot_model(m1, show.values = TRUE, value.offset = .3)
```



# HR for 30- d mortality
```{r}
m1 <- coxph(Surv(Time, Death30) ~ factor(Coinfection)+age+sex+Asplenia+CHF+COPD+Diabetes+Hypertension+Chronic.Kidney.Disease+Lymphoma+Rheumatoid.Arthritis+Obesity+Depression+Blood_Loss_Anemia+Simple_Blood_Transfusion,  data =  dat)

summary(m1)


aa=exp(cbind(OR = coef(m1), confint(m1)))
aa

plot_model(m1, show.values = TRUE, value.offset = .3)
```





# OR for mortality
```{r}
m1 <- glm(Death90 ~ factor(Coinfection)+age+sex+Asplenia+CHF+COPD+Diabetes+Hypertension+Chronic.Kidney.Disease+Lymphoma+Rheumatoid.Arthritis+Obesity+Depression+Blood_Loss_Anemia+Simple_Blood_Transfusion,  data =  dat,family=binomial(link = logit))

summary(m1)


aa=exp(cbind(OR = coef(m1), confint(m1)))



f=plot_model(m1, show.values = TRUE, value.offset = .3)
summ(m1,exp = TRUE, digit=4)
```



#Logistic regession: ARDS---------------------------------------

```{r}

m1<- glm(ARDS~factor(Coinfection)+age+sex+Asplenia+CHF+COPD+Diabetes+Hypertension+Chronic.Kidney.Disease+Lymphoma+Rheumatoid.Arthritis+Obesity+Depression+Blood_Loss_Anemia+Simple_Blood_Transfusion, data = dat, family=binomial(link = logit))
summary(m1)
aa=exp(cbind(OR = coef(m1), confint(m1)))
aa



f=plot_model(m1, show.values = TRUE, value.offset = .3)
summ(m1,exp = TRUE, digit=4)

```





#Logistic regession: DIC----------------------------------------

```{r}

m1<- glm(DIC~factor(Coinfection)+age+sex+Asplenia+CHF+COPD+Diabetes+Hypertension+Chronic.Kidney.Disease+Lymphoma+Rheumatoid.Arthritis+Obesity+Depression+Blood_Loss_Anemia+Simple_Blood_Transfusion, data = dat, family=binomial(link = logit))
summary(m1)
aa=exp(cbind(OR = coef(m1), confint(m1)))
aa



g=plot_model(m1, show.values = TRUE, value.offset = .3)
summ(m1,exp = TRUE, digit=4)

```




#Logistic regession: MOD---------------------------------------

```{r}

m1<- glm(MOF~factor(Coinfection)+age+sex+Asplenia+CHF+COPD+Diabetes+Hypertension+Chronic.Kidney.Disease+Lymphoma+Rheumatoid.Arthritis+Obesity+Depression+Blood_Loss_Anemia+Simple_Blood_Transfusion, data = dat, family=binomial(link = logit))
summary(m1)
aa=exp(cbind(OR = coef(m1), confint(m1)))
aa


h=plot_model(m1, show.values = TRUE, value.offset = .3)
summ(m1,exp = TRUE, digit=4)

```




```{r}
splots <- list(f,g,h)


LLL=ggarrange(f,g,h + rremove("x.text"), 
          labels = c("A", "B", "C"),
          ncol = 3, nrow = 1)

# Arrange multiple ggsurvplots and print the output
#LL=arrange_ggsurvplots(splots, print = TRUE, labels = c("A","B", "C","D"),
 #nrow = 2,  ncol = 2, risk.table.height = 0.4)


tiff("figs/Fig5.tiff", width=4500, height=2000, res=300, compression = "lzw")
#pdf("figs/Fig5.pdf", width = 20,height = 10)
print(LLL)
dev.off()



Cairo::Cairo(
  60, #length
  30, #width
  file = paste("figs/Figure5", ".TIF", sep = ""),
  type = "TIF", #tiff
  bg = "transparent", #white or transparent depending on your requirement 
  dpi = 300,
  units = "cm" #you can change to pixels etc 
)
plot(LLL) #p is your graph object 
dev.off()





```






```{r}
datb=read.csv("Babesia_timeseries_ssentongo2024.csv", header = T)
```

```{r}
datbb<- datb %>%
  mutate(date = lubridate::mdy(Month))

m1<- glm(Freq~Var2,family=poisson, data = datb) 
summary(m1)

plot_model(m1, show.values = TRUE, value.offset = .3)
summ(m1,exp = TRUE, digit=4)


```




```{r}

g <- datbb %>%
ggplot(aes(date, Freq)) +
  geom_line(color = "magenta", size=2, lty=1) +
    scale_y_continuous(labels = scales::comma)+
  scale_x_date(date_breaks = "4 month",date_labels = "%b-%y") +
  facet_wrap(~ "Trends in Babesiosis cases in the U.S, Oct 2015 - Dec 2022") +
  theme(legend.position = "none") +
  
   theme(text = element_text(size = 20))+
    theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  xlab("Date") + ylab("Monthly counts of Babesia cases")+
  labs(
    title = "",
    subtitle = "",
    caption = "",
    x = "Month and year of infection"
  )
show(g)


g=g+ xlab("Month and year of infection")+
  ylab('Monthly counts of Babesia cases')+
  theme(
    axis.title.x=element_text(angle=0,face='bold',color='black',size = 14),
    axis.title.y=element_text(angle=90, color='black', face='bold', size=14),
    axis.text.x = element_text( color="black",size=14,angle=0),
    axis.text.y = element_text(face="bold", color="black", size=14, angle=0),
    legend.text = element_text(colour="black", size=14,face="bold"),
     strip.text = element_text(size = 14),
    legend.title = element_text(colour="black", size=14,face="bold"))

g=g + stat_smooth(color = "black", fill = "#FC4E07",method = "lm",se=F, size=2)
g



tiff("figs/Fig3.tiff", width=4000, height=2000, res=300, compression = "lzw")
#pdf("figs/Fig3.pdf", width = 30, height = 15)
print(g, newpage = FALSE)
dev.off()



Cairo::Cairo(
  60, #length
  30, #width
  file = paste("figs/Figure3", ".TIF", sep = ""),
  type = "TIF", #tiff
  bg = "transparent", 
  dpi = 300,
  units = "cm" 
)
plot(g) 
dev.off()


```




# Coinfection plot
```{r}
dat1=read.csv("co-infection3_sentongo2024.csv")


p=ggplot(data=dat1, mapping = aes(x = reorder(Infection, -PR), PR))+
  geom_bar(stat="identity", fill="blue")+
   ylim(0, 50)+
  geom_text(aes(label=PR), vjust=-1.4,color="black", size=5)+
     facet_wrap(~ "Rates of coinfections (%)") 
 # theme_minimal()


p=p+ xlab("Co-infection groups")+
  ylab('Prevalence rate of Babesia coinfections (%)')+
  theme(
    axis.title.x=element_text(angle=0,face='bold',color='black',size = 14),
    axis.title.y=element_text(angle=90, color='black', face='bold', size=14),
    axis.text.x = element_text( color="black",size=14,angle=0),
    axis.text.y = element_text(face="bold", color="black", size=14, angle=0),
    legend.text = element_text(colour="black", size=14,face="bold"),
     strip.text = element_text(size = 14),
    legend.title = element_text(colour="black", size=14,face="bold"))

p


tiff("figs/Fig2.TIF", res=300)
print(p, newpage = FALSE)
dev.off()


Cairo::Cairo(
  30, #length
  30, #width
  file = paste("figs/Figure2", ".TIF", sep = ""),
  type = "TIF", #tiff
  bg = "transparent", #white or transparent depending on your requirement 
  dpi = 300,
  units = "cm" 
)
plot(p)
dev.off()


```


